\speculake: Hiding Malware in Speculative Execution

### 2018-11-30 paper/architecture.tex
add reference to new figure and clarify speculative entry point != speculative key
Added description of arbitrary memory read methodology

We explore the ability for the CPU to ``double speculate'', where a second
stalled indirect jump while the CPU is already speculating causes it to predict
the target and
speculate a second time. For instance, suppose a payload program truly jumps to
target A, but the CPU is mistrained by a trigger program that jumps to B, thus
causing the payload program to speculatively execute at B. At B, suppose there
is a second indirect jump, perhaps using the same register as the first jump
(which has still not resolved). If the trigger program jumps to C, the payload
program may speculate a second time and continue speculative execution at~C.

@@

We summarize our findings into a \emph{speculative primitive}, which allows our
payload program to speculatively (and covertly) perform on the order of 100
arbitrary instructions while an accompanying trigger program is running, and
communicate a short (e.g. single byte) result to the real world via a cache side
channel. These speculative instructions are able to read from any real-world
memory or registers, but they cannot perform updates or writes directly. To
update memory, the speculative instructions must communicate to the real world.
We use a cache side channel to do so, but other side channels compatible with
Spectre could also be used~\cite{kiriansky2018speculative}.

>>>>

We explore the ability for the CPU to ``double speculate'', where a second
stalled indirect jump while the CPU is already speculating causes it to predict
the target and speculate a second time. For instance, suppose a payload program
truly jumps to target A, but the CPU is mistrained by a trigger program that
jumps to B, thus causing the payload program to speculatively execute at B. At
B, suppose there is a second indirect jump, perhaps using the same register as
the first jump (which has still not resolved). If the trigger program jumps to
C, the payload program may speculate a second time and continue speculative
execution at~C. Figure~\ref{fig:nested-spec} demonstrates Nested Speculation in
action.

@@

We summarize our findings into a \emph{speculative primitive}, which allows our
payload program to speculatively (and covertly) perform on the order of 100
arbitrary instructions while an accompanying trigger program is running, and
communicate a short (e.g. single byte) result to the real world via a cache side
channel. These speculative instructions are able to read from any cpu state 
accessible to the process in the real world including memory and registers, 
but they cannot perform updates 
or writes directly. To read memory the \emph{speculative primitive} makes use
of the ability to bring things into cache. If a load for an uncached memory 
location is initiated speculatively it will not finish within the speculative 
window (meaning no value can be exfiltrated to the real world). However, the 
memory read is not canceled and the value will be available from cache when 
the processor accesses it speculatively again. To update memory, the speculative 
instructions must communicate to the real world.  We use a cache side channel 
to do so, but other side channels compatible with Spectre could also 
be used~\cite{kiriansky2018speculative}.
